\section{Baked eggs with yoghurt and chilli}
\author{Yotam Ottolenghi in \it{The Guardian}}

\index{arugula}
\index{eggs}

\subsection*{Ingredients (Serves approximately 2)}
\begin{itemize}
  \item 300g rocket (arugula)
  \item 2 tbsp olive oil
  \item 4 free-range eggs
  \item 150g Greek yogurt
  \item 1 garlic clove, peeled and crushed
  \item 50g unsalted butter
  \item 1/2 tsp (more or less, depending on variety) kirmizi biber\footnote{This
    can be subsituted with red chilli flakes and paprika} 
  \item 6 sage leaves, shredded
  \item Maldon sea salt
\end{itemize}

Preheat the oven to 150C/300F/gas mark 2. Wash the rocket and place with the oil in a large pan, add some salt and sauté over medium heat for about five minutes, or until the rocket has wilted and most of the liquid has evaporated.

Transfer the contents of the frying pan to a small, ovenproof dish and make four deep indentations in the rocket mix. Carefully break an egg into each crater, taking care not to break the yolk. Place in the oven for 10-15 minutes, or until the egg whites set.

While the eggs are in the oven, mix together the yogurt and garlic along with a pinch of salt. Stir well, taste, adjust the seasoning if necessary and set aside - do not chill, however.

Melt the butter in a small saucepan, add the kirmizi biber and a pinch of salt, and fry for a minute or two or until the butter starts to foam and turns a nice golden-red. Add the sage, cook for a few seconds longer, then remove from the heat.

Once the eggs are done, take the dish out of the oven. Spoon the yogurt mix over the centre, and pour the hot chilli butter over the yogurt and eggs. Serve piping hot.

